\documentclass[10pt]{article}

\newcommand{\littleblank}{\rule{.5in}{.01in}}
\newcommand{\blank}{\rule{1in}{.01in}}
\newcommand{\bigblank}{\rule{2in}{.01in}}
\newcommand{\bigbigblank}{\rule{3in}{.01in}}
\newcommand{\CUT}[0]{}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subfig} 
\usepackage{bm}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{PID: \underline{\hspace{1in}}}

\vspace{.1in}
\begin{document}

\setlength\parindent{0pt}
\thispagestyle{empty}

{\textbf \Large Quiz 3} \hfill CSE 255, Spring 2017
\\

\vspace{.1in}

Name: \underline{\hspace{3in}}
\\

PID: \underline{\hspace{3.15in}}

\vspace{.1in}

{\small \setlength\parindent{20pt}This is the third quiz of CSE255/DSE230

On your desk you should have only the exam paper and writing tools.
No hats or hoods allowed (unless religious items).
There are 2 questions in this exam, totalling 100 points.

You have 10 minutes to complete the exam.

Start by writing your name and PID on this page.

Good Luck!}\\
\underline{\hspace{6in}}

\newcommand{\uu}{\vec{u}}
\newcommand{\xx}{\vec{x}}
\newcommand{\yy}{\vec{y}}

\vspace{.1in}
\noindent
{\bf I. (25 points) Orthonormal basis} \\
Suppose that $V$ is a vector space of dimension $d$, that
$\uu_1,\uu_2,\ldots,\uu_d$ is a basis for $V$, and that $\xx \in V$ is
an arbitrary vector in $V$. Express $\xx$ as a linear combination of
the basis vectors.\\
~\\
\underline{$\xx=$\hspace{6in}}\\
~\\
\vspace{.1in}
\noindent
{\bf II. (25 points) Eigen-Vectors} \\
Suppose $M$ is a symmetric (real valued) $d \times d$ matrix, that
$((\uu_1,\lambda_1),(\uu_2,\lambda_2),\ldots,(\uu_d,\lambda_d))$  are
eigen-vector,eigen-value pairs. The eigen-values are all different.\\
~\\
Mark all of the correct statements:
\begin{enumerate}
\item For any $i$: $M \uu_i = \lambda_i \uu_i$
\item For any $i$: $\uu_i \cdot \uu_i =1$
\item For any $i \neq j$: $\uu_i \cdot \uu_j=0$
\item The set $\uu_1,\ldots \uu_d$ forms a basis of $R^d$.
\end{enumerate}

\vspace{.1in}
\noindent
{\bf III. (25 points) The covariance matrix}\\
Suppose you have $N$ vectors in $R^d$: $\xx_1,\ldots,\xx_N$. $\xx_i$
are column vectors.\\
~\\
Write an expression for the expected vector\\
~\\
\underline{$\vec{\mu} = $\hspace{6in}}
~\\
Write an expression for the Covariance matrix\\
~\\
\underline{$C = $\hspace{6in}}

\vspace{.1in}
\noindent
{\bf IV. (25 points)  PCA} \\
Suppose $C$ is a covariance matrix computed for the dataset
$\xx_1,\ldots,\xx_N$. Suppose that non of the eigenvalues of $C$ is
zero. Suppose $U$ is the orthonormal matrix
that contains the eigenvctors of $C$. $U$ can be seen as a change of
basis. Define the transformed dataset to be $\yy_i = U \xx_i$. What
can you say about the covariance matrix of the dataset:
$\yy_1,\ldots,\yy_N$?\\
~\\
\underline{\hspace{6in}}

\end{document}   




 
