\documentclass[10pt]{article}

\newcommand{\littleblank}{\rule{.5in}{.01in}}
\newcommand{\blank}{\rule{1in}{.01in}}
\newcommand{\bigblank}{\rule{2in}{.01in}}
\newcommand{\bigbigblank}{\rule{3in}{.01in}}
\newcommand{\CUT}[0]{}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subfig} 
\usepackage{bm}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{PID: \underline{\hspace{1in}}}

\vspace{.1in}
\begin{document}

\setlength\parindent{0pt}
\thispagestyle{empty}

{\textbf \Large Quiz 8} \hfill CSE 255, Spring 2017
\\

\vspace{.1in}

Name: \underline{\hspace{3in}}
\\

PID: \underline{\hspace{3.15in}}

\vspace{.1in}

{\small \setlength\parindent{20pt}This is the 8th quiz of CSE255/DSE230

  On your desk you should have only the exam paper and writing tools.
  
No hats or hoods allowed (unless religious items).

There are 5 questions in this quiz, each worth 20 points.

You have 20 minutes to complete the exam.

Start by writing your name and PID on this page.

Good Luck!}\\
\underline{\hspace{6in}}

\newcommand{\uu}{\vec{u}}
\newcommand{\xx}{\vec{x}}
\newcommand{\yy}{\vec{y}}
\newcommand{\vmu}{\vec{\mu}}
~\\
~\\
\noindent
   Define an $\epsilon$-cover of a set
    $S$ to be a set balls of radius $\epsilon$ that
    cover the set (i.e. $S$ is a subset of the union of the
    balls). Let $N(\epsilon)$ be the {\em minimal} number of balls of
    radius $\epsilon$ needed to cover $S$.
    Define the {\bf intrinsic dimension} of $S$ to be the minimal value of
    $d$ such that there exists a positive, finite, real number $C$
    such that:
    $$\forall \epsilon>0, \;\; N(\epsilon)< \frac{C}{\epsilon^d}$$ 
    ~\\
    \newcommand{\vx}{\vec{x}}
    \newcommand{\va}{\vec{a}}
    \newcommand{\vb}{\vec{b}}
    Let $\va,\vb$ be independent vectors in $R^D$. In all of the
    questions below, assume $\|\vx\|_2\leq 100$.\\
    ~\\
    What is the intrinsic dimension of the following sets?
    \begin{enumerate}
    \item $\left\{ \alpha \va \;\;\;\mbox{such that}\;\;\;\alpha
      \mbox{ is an integer between -100 and +100} \right\}$ \underline{\hspace{3.15in}}

    \item $\{\alpha \va + \beta \vb\;\;\;\mbox{such
      that}\;\;\;\alpha,\beta\; \mbox{are real numbers, and }|\alpha|+|\beta| \leq 1\}$  \underline{\hspace{3.15in}}
    \item $\{\alpha \va \;\;\;\mbox{such that}\;\;\; \alpha \mbox{ is
      a real number } 0 \leq \alpha \leq 1 \}$  \underline{\hspace{3.15in}}
    \item $\{\vx\;\;\;\mbox{such that}\;\;\;\vx \cdot \va = 5\}$ \underline{\hspace{3.15in}}
    \item $\{\vx\;\;\;\mbox{such that}\;\;\;\vx \cdot \va = 5
      \;\;\mbox{and}\;\; \vx \cdot \vb > 0\}$ \underline{\hspace{3.15in}}
    \end{enumerate}
\end{document}   




 
