\documentclass[11pt]{article}

\newcommand{\littleblank}{\rule{.5in}{.01in}}
\newcommand{\blank}{\rule{1in}{.01in}}
\newcommand{\bigblank}{\rule{2in}{.01in}}
\newcommand{\bigbigblank}{\rule{3in}{.01in}}
\newcommand{\CUT}[0]{}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subfig} 
\usepackage{bm}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{PID: \underline{\hspace{1in}}}

\vspace{.1in}
\begin{document}

\setlength\parindent{0pt}
\thispagestyle{empty}

{\textbf \Large Quiz 2} \hfill CSE 255, Spring 2017
\\

\vspace{.1in}

Name: \underline{\hspace{3in}}
\\

PID: \underline{\hspace{3.15in}}

\vspace{.1in}

{\small \setlength\parindent{20pt}This is the second quiz of CSE255/DSE230

On your desk you should have only the exam paper and writing tools.
No hats or hoods allowed (unless religious items).
There are 2 questions in this exam, totalling 100 points.
Circle all correct answers.

You have 5 minutes to complete the exam.

Start by writing your name and PID on this page.

Good Luck!}

\vspace{.2in}
\noindent
I. (20 points)  Lazy evaluation: \\
Mark {\bf all} correct answers
\begin{enumerate}
\item Has lower memory requirements than Busy evaluation.
\item Requires fewer scans of memory than Busy evaluation.
\item Stores intermediate results.
\end{enumerate}


\vspace{.1in}
\noindent
II. (80 points) Consider the following code snippet:
\begin{verbatim}
1> X=sc.paralellize(range(3000000))
2> Y=X.map(lambda x: (x,cos(x)*sin(x))).cache()
3> Z=X.map(lambda x: (x,cos(x)*sin(x)))
4> print Y.reduce(lambda x,y:x+y)
5> print Y.reduce(lambda x,y:x+y)
6> print Z.reduce(lambda x,y:x+y)
7> print Z.reduce(lambda x,y:x+y)
\end{verbatim}
Mark {\bf all} correct answers
\begin{enumerate}
\item Line 1 will take significantly more time than line 2
\item Line 2 will take significantly more time than line 3
\item Line 6 will take significantly more time than line 4
\item Line 6 will take significantly more time than line 7
\item Line 7 will take significantly more time than line 4
\item Line 4 will take significantly more time than line 5
\end{enumerate}

\end{document}   




 
