\documentclass[11pt]{article}


\newcommand{\littleblank}{\rule{.5in}{.01in}}
\newcommand{\blank}{\rule{1in}{.01in}}
\newcommand{\bigblank}{\rule{2in}{.01in}}
\newcommand{\bigbigblank}{\rule{3in}{.01in}}
\newcommand{\CUT}[0]{}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subfig} 
\usepackage{bm}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{PID: \underline{\hspace{1in}}}

\vspace{.1in}
\begin{document}

\setlength\parindent{0pt}
\thispagestyle{empty}

{\textbf \Large Quiz 1} \hfill CSE 255, Spring 2017
\\

\vspace{.1in}

Name: \underline{\hspace{3in}}
\\

PID: \underline{\hspace{3.15in}}

\vspace{.1in}

{\small \setlength\parindent{20pt}This is the first quiz of CSE255/DSE230

On your desk you should have only the exam paper and writing tools.

No hats or hoods allowed (unless religious items).

There are 4 questions in this exam, totalling 100 points.

Circle the correct answers.

You have 5 minutes to complete the exam.

Start by writing your name and PID on this page.

Good Luck!}

\vspace{.1in}

\noindent
I. Which types of locality take advantage of the fact that disk read
heads move slowly? (
\begin{enumerate}
\item Temporal Locality
\item Spatial Locality
\item Neither Temporal nor Spatial
\item Both Temporal and Spatial
\end{enumerate}

\vspace{.1in}
\noindent
Consider the following code snippet:
\begin{verbatim}
X=range(1000000)
s=0
for i in range(1000000):
   s+=X[i]
\end{verbatim}

\vspace{.1in}
\noindent
II. Which variables benefit from temporal locality? \underline{\hspace{3.15in}}

\vspace{.1in}
\noindent
III. Which variables benefit from Spatial locality? \underline{\hspace{3.15in}}

\vspace{.1in}
\noindent
IV. Consider the storage of machine level commands. With respect to that
storage, does the code snippet exhibit
\begin{enumerate}
\item Temporal Locality
\item Spatial Locality
\item Neither Temporal nor Spatial
\item Both Temporal and Spatial
\end{enumerate}


\iffalse
\fi
\end{document}   




 
