\documentclass[10pt]{article}

\newcommand{\littleblank}{\rule{.5in}{.01in}}
\newcommand{\blank}{\rule{1in}{.01in}}
\newcommand{\bigblank}{\rule{2in}{.01in}}
\newcommand{\bigbigblank}{\rule{3in}{.01in}}
\newcommand{\CUT}[0]{}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subfig} 
\usepackage{bm}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{PID: \underline{\hspace{1in}}}

\vspace{.1in}
\begin{document}

\setlength\parindent{0pt}
\thispagestyle{empty}

{\textbf \Large Quiz 7} \hfill CSE 255, Spring 2017
\\

\vspace{.1in}

Name: \underline{\hspace{3in}}
\\

PID: \underline{\hspace{3.15in}}

\vspace{.1in}

{\small \setlength\parindent{20pt}This is the 7'th quiz of CSE255/DSE230

On your desk you should have only the exam paper and writing tools.
No hats or hoods allowed (unless religious items).
There is one question in this quiz.

You have 15 minutes to complete the exam.

Start by writing your name and PID on this page.

Good Luck!}\\
\underline{\hspace{6in}}

~\\
~\\
\noindent

   Suppose examples are generated in the following way. The input
   feature $x$ is a scalar drawn uniformly from the range
   $[0,1]$. The label is one of ${+1,-1}$ and is generated
   according to the conditional probability
   $$P(y=+1 | x) = \left[ax +b\right]$$ where $a,b>0$ are unknown
   parameters and the square
   brackets indicate restricting the variable between $0$ and $1$
   $$[x] = \max(0,\min(x,1))$$. You are given a training set,
   generated IID according to the given distribution:
   $(x_1,y_1),(x_2,y_2),\ldots,(x_m,y_m)$

   \begin{enumerate}
   \item Write an expression for the Bayes optimal rule.
     \\~\\
     \underline{\hspace{6in}}
   \item Write an expression for the Bayes error (the error of the
     Bayes optimal rule).
     \\~\\
     \underline{\hspace{6in}}
   \item What would you try to estimate if you were using 
     generative models?
     \\~\\
     \underline{\hspace{6in}}
   \item What set of rules should you consider if you were using
     discriminative models?
     \\~\\
     \underline{\hspace{6in}}
   \item What would be the optimal discriminative rule?
     \\~\\
     \underline{\hspace{6in}}
   \end{enumerate}

\end{document}   




 
