\documentclass[10pt]{article}

\newcommand{\littleblank}{\rule{.5in}{.01in}}
\newcommand{\blank}{\rule{1in}{.01in}}
\newcommand{\bigblank}{\rule{2in}{.01in}}
\newcommand{\bigbigblank}{\rule{3in}{.01in}}
\newcommand{\CUT}[0]{}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subfig} 
\usepackage{bm}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{PID: \underline{\hspace{1in}}}

\vspace{.1in}
\begin{document}

\setlength\parindent{0pt}
\thispagestyle{empty}

{\textbf \Large Quiz 5} \hfill CSE 255, Spring 2017
\\

\vspace{.1in}

Name: \underline{\hspace{3in}}
\\

PID: \underline{\hspace{3.15in}}

\vspace{.1in}

{\small \setlength\parindent{20pt}This is the fifth quiz of CSE255/DSE230

On your desk you should have only the exam paper and writing tools.
No hats or hoods allowed (unless religious items).
There is one question in this quiz.

You have 10 minutes to complete the exam.

Start by writing your name and PID on this page.

Good Luck!}\\
\underline{\hspace{6in}}

\newcommand{\uu}{\vec{u}}
\newcommand{\xx}{\vec{x}}
\newcommand{\yy}{\vec{y}}
\newcommand{\vmu}{\vec{\mu}}
~\\
~\\
\noindent
    This problem regards the following concepts
    \begin{itemize}
      \item the K-means {\bf cost function}, which is the
    average distance between each point and its closest
    representative.
    \item The K-means {\bf problem}, which is the
    problem of finding the set of $k$ representatives that minimizes
    the cost function.
    \item The K-means {\bf algorithm} which is an algorithm for
      iteratively improving the cost function.
    \item We say that an the K-means algorithm has
    {\bf converged} if the assignment of points to representatives does not
    change from one iteration to the next.
    \item {\bf Simplifying assumption:} assume it is never the case
      that a point has two closest representatives. In other words
      there is always a unique closest representative for each point.
    \end{itemize}
    ~\\
    ~\\
    Mark all of the correct statements
    \begin{itemize}
      \item When using the K-means algorithm, each step before
        convergence is guaranteed to reduce the cost. 
    \item K-means algortihm is guaranteed to converge.
    \item If the K-means algorithm converges, it found a solution to
      the K-means problem.
    \item The K-means algrithm solves the K-means problem.
    \item If there is a poly-time algorithm for the K-means
      problem, then there is a poly-time algorithm for the decision
      version of the travelling salesman problem.
    \end{itemize}

\end{document}   




 
